---
title: "Hackathon"
author: "Manish"
date: "10 November 2017"
output: html_document

---

Define your data exploration, imputation and visualization approach - data in compensation_level has been imputed from 4 levels to 2 levels and the correlation table has been plotted.

```{r}
library(corrplot)
library(knitr)
library(ggplot2)
library(dplyr)
library(class)
library(tree)
library(e1071)


model_DT <- read.csv(file="Model_Data.csv",header=TRUE)

correlation <- select(model_DT,c("Age","fnlwgt","education_number","capital.gain","capital.loss","hours_per_week"))

corr_values <- (cor(correlation))

ggplot(correlation,aes(x=Age,y=fnlwgt))+geom_point()+geom_smooth()

#View(corr_values)

a <- corrplot(corr_values, method = "square")
```


Decision Tree based model

Model1=tree_model_train<-tree(Compensational_level1~.,data=model_data_train)

model1_accuracy=85%

```{r}


setwd("C:/Users/Administrator/Desktop/Manish/Manish/TERM 2/Machine Learning/Hackathon")

model_DT <- read.csv(file="Model_Data.csv",header=TRUE)

model_DT$Compensational_level1 <- gsub("\\.","",model_DT$Compensational_level)

model_DT$Compensational_level1 <- as.factor(model_DT$Compensational_level1)

model_DT <- model_DT[,-c(14,15)]

str(model_DT)

```

```{r}

set.seed(52)

sample_DT <- sample.int(n=nrow(model_DT),size=floor(0.8*nrow(model_DT)),replace=F)

model_data_train<-model_DT[sample_DT,]

#model_data_train$native.country <- NULL

model_data_test<-model_DT[-sample_DT,]

tree_model_train<-tree(Compensational_level1~.,data=model_data_train)

plot(tree_model_train)

text(tree_model_train)

DT_prediction<-predict(tree_model_train,model_data_test)

maxidx=function(arr)
{
  return(which(arr==max(arr)))
}

idx=apply(DT_prediction,c(1),maxidx)

prediction_DT=c('No','Yes')[idx]

confmat_DT=table(prediction_DT,model_data_test$Compensational_level1)

accuracy_DT=sum(diag(confmat_DT))/sum(confmat_DT)

accuracy_DT

```


MODEL2=model_predict_NB <- naiveBayes(Compensational_level1~.,data = sample_model_NB_train)

Model2_accuracy=83%

```{r}
model_NB <- read.csv(file="Model_Data.csv",header=TRUE)

model_NB$Compensational_level1 <- gsub("\\.","",model_NB$Compensational_level)

model_NB$Compensational_level1 <- as.factor(model_NB$Compensational_level1)

model_NB <- model_NB[,-c(14,15)]

set.seed(52)

sample_NB <- sample.int(n=nrow(model_NB),size=floor(0.8*nrow(model_NB)),replace=F)

sample_model_NB_train <- model_NB[sample_NB,]

sample_model_NB_test <- model_NB[-sample_NB,]

model_predict_NB <- naiveBayes(Compensational_level1~.,data = sample_model_NB_train)

pred_NB <- predict(model_predict_NB,sample_model_NB_test)

confmat_NB <- table(pred_NB,sample_model_NB_test$Compensational_level1)

accuracy_NB=sum(diag(confmat_NB))/sum(confmat_NB)

accuracy_NB

```



KNN based model

MOdel3=KNN_pred_label <- knn(train=model_KNN_train,test=model_KNN_test,cl=model_KNN_train_label,k)

MOdel3_accuracy=77%

```{r}

model_KNN <- read.csv(file="Model_Data.csv",header=TRUE)


model_KNN$Compensational_level1 <- gsub("\\.","",model_NB$Compensational_level)

model_KNN$Compensational_level1 <- as.factor(model_KNN$Compensational_level1)

model_KNN$native.country <- as.factor(model_KNN$native.country)

model_KNN$native.country <- as.integer(model_KNN$native.country)

model_KNN <- model_KNN[,-15]

model_KNN

str(model_KNN)

model_KNN$workclass <- as.integer(model_KNN$workclass)

model_KNN$education <- as.integer(model_KNN$education)

model_KNN$marital_status <- as.integer(model_KNN$marital_status)

model_KNN$occupation <- as.integer(model_KNN$occupation )

model_KNN$relationship <-  as.integer(model_KNN$relationship)

model_KNN$race <- as.integer(model_KNN$race)

model_KNN$sex <- as.integer(model_KNN$sex)


set.seed(28)

randon_sample_KNN <- sample.int(n=nrow(model_KNN),size=floor(0.8*nrow(model_KNN)),replace=F)
  
model_KNN_train <- model_KNN[randon_sample_KNN,(1:14)]

model_KNN_test<-model_KNN[-randon_sample_KNN,(1:14)]

model_KNN_train_label<-model_KNN[randon_sample_KNN,15]

model_KNN_test_label<-model_KNN[-randon_sample_KNN,15]


k=6


KNN_pred_label <- knn(train=model_KNN_train,test=model_KNN_test,cl=model_KNN_train_label,k)

confmatrix_KNN=table(model_KNN_test_label,KNN_pred_label)

accuracy_KNN<-sum(diag(confmatrix_KNN)/sum(confmatrix_KNN))  

accuracy_KNN


```

